Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-02-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\begin{abstract} 
%CAUSE --> EFFECT --> MOTIVATION (P1)
  A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient. Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which understandiing the dynamics of immiscible fluid displacement may help mitigating water resources contamination and improving hydrocarbons production. Due to the large viscosity ratio, flow instabilities at fluids' interface may arise leading to formation and growth of fingers, with strong impact on the displacement efficiency.  
%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)

The main aim of this work is to numerically investigate

>>>>

\begin{abstract} 
%CAUSE --> EFFECT --> MOTIVATION (P1)
  A critical aspect of multiphase flows in porous media is the displacement efficiency that measures the amount of fluid that can be pushed by another fluid driven by pressure gradient. Migration of contaminants and waterflooding/EOR (enhanced oil recovery) are typical applications in which understandiing the dynamics of immiscible fluid displacement may help mitigating water resources contamination and improving hydrocarbons production. Due to the large viscosity ratio, flow instabilities at fluids' interface may arise leading to formation and growth of fingers, with strong impact on the displacement efficiency.  
%CAUSE --> EFFECT --> GAPS IN KNOWLEDGE --> AIMS OF THE WORK (P2)
Initial studies of viscous instabilities in Hele-Shaw cells indicated that the development of fingers depends mostly on mobility ratio and capillary number, however heterogeneity of the porous domain may affect the onset formation of fingers. Therefore, the main aim of this work is to numerically investigate formation and growth of viscous fingers in heterogeneous porous media. The model used here is based on a novel control volume finite element method (CVFEM) formulation with a new family of FE-pairs, \PN[n]{m} and \PNDG[n]{m}
